\documentclass[10pt]{letter}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{setspace}

% Adjust spacing
\renewcommand{\baselinestretch}{1.1}

% Sender information
\signature{Dominic Lacaille}
\address{Montreal, Canada \\ Email: dominic@lacaille.app \\ Phone: +1 (514) 984-0393 \\ LinkedIn: \href{https://linkedin.com/in/dominic-lacaille-mtl}{linkedin.com/in/dominic-lacaille-mtl}}

\begin{document}

\begin{letter}{Hiring Manager \\ Hospitality Team \\ Lightspeed Commerce \\ Montreal}  

\opening{Dear Hiring Manager,}

I am writing to express my enthusiasm for the Senior Front-End Developer role at Lightspeed. With 14 years of experience designing and developing web, mobile, and server applications, I bring a proven ability to translate functional requirements into robust, scalable solutions. My strong problem-solving skills and aptitude for tackling complex challenges have been instrumental in delivering impactful software for various industries.

In my current role as Senior Developer at Solution-Tek, I:

\begin{itemize}
  \item Designed and implemented a microservices-based system in C\# and RabbitMQ, enabling high-volume reaccommodation of airline passengers.
  \item Developed a React frontend in TypeScript to manage disrupted flights and passengers, achieving a 300\% performance improvement through architectural enhancements.
  \item Championed cloud-native solutions, ensuring high availability and reliability on Amazon Web Services.
  \item Collaborated with cross-functional teams to implement heuristics for finding alternate flights, aligning with complex airline rules.
\end{itemize}

These achievements underscore my ability to lead technical initiatives, enhance system performance, and deliver user-focused solutions. I thrive in environments where innovation and collaboration drive success, and I am eager to bring this mindset to the Hospitality team at Lightspeed.

What excites me most about the Hospitality Team is that my previous experience in mass airline passenger reaccommodation might prove very useful in the domain of Hospitality. I am confident that my experience and passion for building high-quality scalable software aligns with your organization's goals.

To add an example, as part of my job we had to automatically evaluate eligibility for hotel accommodations for every disrupted passenger of the airline, which was a very interesting challenge to implement.

I would welcome the opportunity to discuss how my skills and experience can contribute to the success of Lightspeed. Thank you for considering my application. I look forward to the possibility of contributing to your team and would be happy to provide further details during an interview.

\closing{Sincerely,}

\end{letter}

\end{document}


